One exact and one random sampling method to assess the reliability of inferences from network enrichment analysis

### 2018-05-07 doc/genesetdp.tex
edited key words.
specification of null.

\subjclass{G.3. Probabilistic algorithms (including Monte Carlo)}% mandatory: Please choose ACM 1998 classifications from http://www.acm.org/about/class/ccs98-html . E.g., cite as "F.1.1 Models of Computation".
\keywords{Gene Set Enrichment Analysis; Null model; p value; Sampling}% mandatory: Please provide 1-5 keywords

@@

Hence, here we employ a null model of the form ``The query genes are randomly selected the genome``. We present a dynamic programming algorithm, that we dubbed GeneSetDP, that calculates the exact score distribution of any query of a given size. We also implemented one random sampling algorithm for the same task, that we called GeneSetMC.
The algorithms enabled us to calculate well-defined statistics of inferences from NEA.  Using simulations we demonstrated that both the algorithms produced unbiased statistics.

>>>>

\subjclass{G.3. Probabilistic algorithms (including Monte Carlo)}% mandatory: Please choose ACM 1998 classifications from http://www.acm.org/about/class/ccs98-html . E.g., cite as "F.1.1 Models of Computation".
\keywords{Gene Set Analysis; Calibration; Null model; p value; Sampling}% mandatory: Please provide 1-5 keywords

@@

Hence, here we employ a different null model, more directly aimed at model lack of association between query and pathway gene sets, which we formulate as ``The query genes are randomly selected the genome''. We present a dynamic programming algorithm, that we dubbed GeneSetDP, that calculates the exact score distribution of any query of a given size. We also implemented one random sampling algorithm for the same task, that we called GeneSetMC.
The algorithms enabled us to calculate well-defined statistics of inferences from NEA.  Using simulations we demonstrated that both the algorithms produced unbiased statistics.
